---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# LAGOSNEgis

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable) [![CRAN status](https://www.r-pkg.org/badges/version/LAGOSNEgis)](https://cran.r-project.org/package=LAGOSNEgis) [![Travis build status](https://travis-ci.org/cont-limno/LAGOSNEgis.svg?branch=master)](https://travis-ci.org/cont-limno/LAGOSNEgis) [![DOI](https://zenodo.org/badge/106293356.svg)](https://zenodo.org/badge/latestdoi/106293356)



Extra functions to interact with the GIS module of LAGOSNE.

## Features

* **Easy**: Convenience functions allow for straight-forward subsetting.

* **Fast**: Queries are optimized for speed to avoid loading the entirety of massive layers. 

* **Flexible** : Custom queries can be constructed using `SQL` statements.

## Installation

```{r eval=FALSE}
remotes::install_github("cont-limno/LAGOSNEgis")
```

## Usage

```{r eval=FALSE}
library(LAGOSNEgis)
```

### Download data

```{r eval=FALSE}
lagosnegis_get()
```

### List available GIS layers

```{r eval=FALSE}
library(sf)
sf::st_layers(LAGOSNEgis:::lagosnegis_path())
```

```{r eval = FALSE, echo=FALSE}
ly <- sf::st_layers(LAGOSNEgis:::lagosnegis_path())
knitr::kable(data.frame(ly[c("name", "driver", "features", "fields")]))
```

### Query from a specfic layer

```{r eval=FALSE}
res_iws  <- query_gis(layer = "IWS", 
                      id_name = "lagoslakeid", ids = c(34352))
res_lake <- query_gis(layer = "LAGOS_NE_All_Lakes_4ha", 
                      id_name = "lagoslakeid", ids = 34352)
res_pnt  <- query_gis(layer = "LAGOS_NE_All_Lakes_4ha_POINTS", 
                      id_name = "lagoslakeid", ids = 34352)
```

### Query a combined watershed and lake polygon

```{r eval=FALSE}
res <- query_wbd(lagoslakeid = c(7010))
```

### Flexible queries using `SQL` statements

```{r eval=FALSE}
res <- query_gis_(query = "SELECT * FROM IWS WHERE lagoslakeid IN ('7010');")
```

## References
Soranno P., K. Cheruvelil. 2017. LAGOS-NE-GIS v1.0: A module for LAGOS-NE, a multi-scaled geospatial and temporal database of lake ecological context and water quality for thousands of U.S. Lakes: 2013-1925. Environmental Data Initiative. http://dx.doi.org/10.6073/pasta/fb4f5687339bec467ce0ed1ea0b5f0ca. Dataset accessed 9/26/2017.
